%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {STAFF ENGINEER} % Job title
    {MoneyLion} % Organization
    {Kuala Lumpur, Malaysia} % Location
    {Dec. 2020 - June. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the MoneyLion Mobile Design System, promoting consistency and faster development across platforms.}
        \item {Architected high-impact features and optimized mobile performance to support 10× normal traffic during major campaigns.}
        \item {Drove Apple Pay and Google Pay integration by mentoring payments engineers and guiding secure implementation.}
        \item {Introduced process improvements including in-house bug reporting system that reduced bug cycles by 40\%, TDD adoption, and automated CI/CD workflows.}
        \item {Mentored 10+ junior engineers and helped enhance the hiring and onboarding process.}
        \item {Maintained and scaled the Node.js and Express.js middleware layer, optimizing API performance to support growing user traffic.}
        \item {Received the Lion Heart Award and CEO recognitions for technical leadership and business impact.}
        \item {Tech stack: React Native, TypeScript, Node.js, Express.js, Bitrise (CI/CD), iOS, Android, Apple Pay, Google Pay.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SENIOR IOS SOFTWARE ENGINEER} % Job title
    {Dahmakan} % Organization
    {Kuala Lumpur, Malaysia} % Location
    {June. 2018 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led end-to-end development and deployment of Dahmakan iOS app, managing bi-weekly releases to 500K+ active users with 98\% uptime.}
        \item {Architected and deployed the Dahmakan Rider React Native app (iOS and Android), improving courier engagement by 35\% and reducing delivery time by 20\%.}
        \item {Collaborated with Design, Product, and Backend teams to translate requirements into production features while maintaining high code quality.}
        \item {Optimized app performance and user experience, reducing crash rate by 50\% and improving retention metrics across both platforms.}
        \item {Tech stack: iOS (Swift + Objective-C), Core Data, React Native, MobX, Flexbox, Bitrise (CI/CD), JIRA.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IOS ENGINEER} % Job title
    {UMAI Restaurant Software} % Organization
    {Kuala Lumpur, Malaysia} % Location
    {Oct. 2017 - June. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained UMAI-For-Restaurants iPad application, enabling 200+ restaurant partners to streamline operations and reduce order processing by 25\%.}
        \item {Collaborated with Design and Product teams to identify and resolve restaurant-specific pain points, achieving 4.5-star app rating.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SOFTWARE ENGINEER / DEVELOPER} % Job title
    {Cuelogic Technologies \& Winjit Technologies} % Organization
    {Pune \& Nashik, India} % Location
    {Jul. 2015 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed multiple iOS applications including Social Chat app with real-time messaging, IoT-enabled kitchen appliance app, and consumer-facing apps with 20K+ combined downloads.}
        \item {Mentored junior developers on Swift, Auto-layout, and iOS architecture while managing full development lifecycle from prototyping to production deployment.}
        \item {Received multiple performance awards for technical excellence, achieving 95\% on-time delivery and strong client satisfaction ratings.}
      \end{cvitems}
    }

\end{cventries}
